Comparison to Christensen et al. 2018

### 2023-09-16 doc/paper-comparison.Rmd
l

---
title: "Comparison to Christensen et al. 2018"
author: "Renata Diaz, Juniper Simonis, and Hao Ye"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{paper-comparison}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
params:
  run_models: FALSE
---

@@

This document provides a side-by-side comparison of **`LDATS`** (version 0.3.0) results with analysis from [Christensen et al. 2018](https://esajournals.onlinelibrary.wiley.com/doi/full/10.1002/ecy.2373). 
Due to the size and duration of model runs, we use pre-generated model output from the [LDATS-replications repo](https://github.com/weecology/LDATS-replications).

@@

![plot of chunk plot-paper-LDA](figure/plot-paper-LDA-1.png)

@@

![plot of chunk plot-LDATS-LDA](figure/plot-LDATS-LDA-1.png)

@@

![plot of chunk plot paper LDA and LDATS cpts](figure/plot paper LDA and LDATS cpts-1.png)

@@

![plot of chunk plot ldats LDA and LDATS cpt](figure/plot ldats LDA and LDATS cpt-1.png)

@@

![plot of chunk plot paper LDA and LDATS cpts2](figure/plot paper LDA and LDATS cpts2-1.png)

@@

![plot of chunk plot LDATS lda and paper cpt2](figure/plot LDATS lda and paper cpt2-1.png)

>>>>

---
title: "Comparison to Christensen et al. 2018"
author: "Renata Diaz, Juniper Simonis, and Hao Ye"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Comparison to Christensen et al. 2018}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
params:
  run_models: FALSE
  rmarkdown.html_vignette.check_title: FALSE
---

@@

This document provides a side-by-side comparison of **`LDATS`** (version 0.2.7) results with analysis from [Christensen et al. 2018](https://esajournals.onlinelibrary.wiley.com/doi/full/10.1002/ecy.2373). 
Due to the size and duration of model runs, we use pre-generated model output from the [LDATS-replications repo](https://github.com/weecology/LDATS-replications).

@@

![plot of chunk plot_paper_LDA](figure/plot_paper_LDA-1.png)

@@

![plot of chunk plot_LDATS_LDA](figure/plot_LDATS_LDA-1.png)

@@

![plot of chunk plot_paper_LDA_and_LDATS_cpts](figure/plot_paper_LDA_and_LDATS_cpts-1.png)

@@

![plot of chunk plot_ldats_LDA_and_LDATS_cpt](figure/plot_ldats_LDA_and_LDATS_cpt-1.png)

@@

![plot of chunk plot_paper_LDA_and_LDATS_cpts2](figure/plot_paper_LDA_and_LDATS_cpts2-1.png)

@@

![plot of chunk plot_LDATS_lda_and_paper_cpt2](figure/plot_LDATS_lda_and_paper_cpt2-1.png)
